### 2021-12-02 ms_rbc_dfd/Tex/Sec_Method.tex
dfd talk done

%---------------------------------------------------------------------------%
\lecture{Research Presentation}{lec_present_method}
%---------------------------------------------------------------------------%
\section{\enorcn{Methods}{研究方法}}
%---------------------------------------------------------------------------%
\begin{frame}[fragile]
    \frametitle{Rayleigh's Linear Stability Analysis}
    \begin{itemize}
        \item Assume variables can be decomposed like 
        \begin{align}
            \vec{u}(x, z, t) &= \vec{u'}(x, z, t) \label{EQ:reynolds_dc_u} = u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
            T(x, z, t) &= \overline{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
            p(x, z, t) &= \overline{p}(z, t) +  p'(x, z, t). \label{EQ:reynolds_dc_p}
        \end{align}
        \item The Eigenvalue Problem (EVP) is given by
        \begin{align}
            \nabla \cdot \vec{u'} &= 0 \label{EQ:linear1}\\
            \frac{\partial\vec{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \vec{u'} \label{EQ:linear2}\\
            \frac{\partial T'}{\partial t} + \frac{\partial \overline{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
        \end{align}
    \end{itemize}

@@

        \item We impose \textbf{Marginal Stability} at each timestep
        \begin{equation}
            \max_{k_x} \{ \sigma \} = 0.
        \end{equation}\newline

@@

        \item We evolve the initial (marginally stable) temperature profile $\overline{T}(z,t) \; \longrightarrow \; \overline{T}(z,t+\Delta t)$\newline

@@

        \item Solve $\frac{\partial\overline{T}}{\partial t} + \langle w'T' \rangle_x=0$, yielding $\overline{T}_{adv} \; \longrightarrow \; \sigma_{\rm{adv}}$\newline

        \item Solve $\frac{\partial\overline{T}}{\partial t} = \mathcal{P}\frac{\partial^2 \overline{T}}{\partial z^2}$, yielding $\overline{T}_{adv} \; \longrightarrow \; \sigma_{\rm{diff}}$\newline

@@

>>>>

%---------------------------------------------------------------------------%
\lecture{Research Presentation}{lec_present_method}
%---------------------------------------------------------------------------%
\section{\enorcn{Methods}{研究方法}}
%---------------------------------------------------------------------------%
\begin{frame}[fragile]
    \frametitle{Rayleigh's Linear Stability Analysis}
    \begin{itemize}
        \item Assume variables can be decomposed like 
        \begin{align}
            \vec{u}(x, z, t) &= \vec{u'}(x, z, t) \label{EQ:reynolds_dc_u} = u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
            T(x, z, t) &= \overline{T}(z, t) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
            p(x, z, t) &= \overline{p}(z, t) +  p'(x, z, t). \label{EQ:reynolds_dc_p}
        \end{align}
        \item The linear Eigenvalue Problem (EVP) is given by
        \begin{align}
            \nabla \cdot \vec{u'} &= 0 \label{EQ:linear1}\\
            \frac{\partial\vec{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \vec{u'} \label{EQ:linear2}\\
            \frac{\partial T'}{\partial t} + \frac{\partial \overline{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
        \end{align}
    \end{itemize}

@@

        \item We impose \textbf{Marginal Stability} at each timestep
        \begin{equation}
            \max_{k_x} \{ \sigma \} = 0.
        \end{equation}

@@

        \item We evolve the initial (marginally stable) temperature profile $\overline{T}(z,t) \; \xrightarrow{\text{IVP}} \; \overline{T}(z,t+\Delta t)$\newline

@@

        \item Solve $\frac{\partial\overline{T}}{\partial t} + 2\frac{\partial}{\partial z} \Re\left[ W \theta^* \right] = 0$, yielding $\overline{T}_{adv} \; \xrightarrow{\text{EVP}} \; \sigma_{\rm{adv}}$\newline

        \item Solve $\frac{\partial\overline{T}}{\partial t} = \mathcal{P}\frac{\partial^2 \overline{T}}{\partial z^2}$, yielding $\overline{T}_{adv} \; \xrightarrow{\text{EVP}} \; \sigma_{\rm{diff}}$\newline

@@

\begin{frame}[fragile]
    \frametitle{Multiple Marginally Stable Modes}
    \begin{itemize}
        \item Generalize
        \begin{equation}
            \langle w' T' \rangle_x = \sum_{n = 1}^{N} 2 A_n^2  \Re\left[ W_n \theta_n^* \right] 
        \end{equation}
        to accommodate $N$ simultaneously marginally stable modes\newline

        \item $N$ amplitudes ($\vec{A}\in\mathbb{R}^N$) to maintain marginal stability in $N$ modes
        \begin{equation}
            \vec{\sigma}(\vec{A}) = \vec{0}
        \end{equation} 
        \item Modes with negative amplitudes are not included
    \end{itemize}

\begin{frame}[fragile]
    \frametitle{Solving for the Amplitude Vector $\vec{A}$}
    \begin{enumerate}
        \item Given some guess for the amplitude vector $\vec{A}$ and a fixed timestep $\Delta t$\newline

        \item We construct a Jacobian matrix with finite differences
        \begin{equation}
            J = \begin{bmatrix}
                \nabla \sigma_1 (A_1, A_2, ..., A_N) \\
                \nabla \sigma_2 (A_1, A_2, ..., A_N) \\
                \vdots \\
                \nabla \sigma_N (A_1, A_2, ..., A_N) 
            \end{bmatrix}.
        \end{equation}\newline

        \item Use Newton's method to solve $\vec{\sigma}(\vec{A}) = \vec{0}$
    \end{enumerate}

\begin{frame}[fragile]
    \frametitle{The Amplitude Guess for $N$ modes}
    \begin{itemize}
        \item The amplitude vector can be approximated by
        \begin{equation}
            \vec{A^2} \approx = -\Sigma_{\rm{adv}}^{-1} \vec{\sigma_{\rm{diff}}}.
            \label{EQ:AN_approx}
        \end{equation}
        \item The advective growth rate matrix $\Sigma_{\rm{adv}}$ measures the effect of the $j$th mode's advection on the $i$th mode's growth rate\newline

        \item The diffusive growth rate vector $\vec{\sigma_{\rm{diff}}}$ measures the effect of diffusion on the $i$th mode's growth rate
    \end{itemize}

\end{frame}
%---------------------------------------------------------------------------%
%---------------------------------------------------------------------------%
\begin{frame}[fragile]
    \frametitle{Marginally Stable Thermal Equilibria}
    \begin{itemize}
        \item Evolve until the \textbf{advection} cancels \textbf{diffusion}
        \begin{equation}
            \frac{\partial}{\partial z} \langle w'T' \rangle_x = \mathcal{P} \frac{\partial^2 \overline{T}}{\partial z^2} \quad \longrightarrow \quad \frac{\partial \overline{T}}{\partial t} = 0
        \end{equation}

        \item Such states are referred to as Marginally Stable Thermal Equilibria (MSTE)\newline

        \item We compute symmetric MSTE for $10^6 \leq \rm{Ra}\leq 10^9$

    \end{itemize}
\end{frame}
